Topological Analysis of Bitcoin's Lightning Network

### 2019-01-11 article/main.tex
Approximating power-law exponent

\begin{abstract}
Bitcoin's Lightning Network (LN) is a scalability solution for Bitcoin, which allows transactions to be issued with negligible fees and settle transactions instantly at scale. In order to use LN, funds need to be locked in payment channels on the Bitcoin blockchain (Layer-1), that one may use them in LN (Layer-2). LN is comprised of many payment channels forming a payment channel network. LN promises that a few payment channels already enable anyone to efficiently, securely and privately route payments across the whole network. In this paper we quantify the structural properties of LN and argue that LN's current topological properties largely harms its value proposition and potential.  
\end{abstract}
\keywords{Bitcoin, Lightning Network, Network Topology, Payment Channel Network}

\section{Introduction}
Recently the Bitcoin \cite{nakamoto2008bitcoin} network celebrated its 10th anniversary. During these years Bitcoin gained a huge popularity due to its publicly verifiable, decentralized, permissionless and censorship-resistant nature. This tremendous popularity and increasing interest in Bitcoin pushed its network's throughput to its limits. Without further advancements, the Bitcoin network can only settle $7$ transactions per second (tps), while mainstream centralized payment providers such as Visa and Mastercard can process approximately \num[group-separator={,}]{40000} tps in peak hours. Moreover one might need to pay large transaction fees on the Bitcoin network, while also need to wait 6 new blocks to be published in order to be certain enought that the transaction is included in the blockchain.

@@

\textbf{Our contributions.} We empirically measure and describe LN's topology and show that it is utterly centralized and fragile against both random failures and targeted attacks. These findings suggest that LN, unlike Bitcoin, is undoubtedly far from being reliable, censorship-resistant, decentralized and private.
\section{Lightning Network's Topology}
\begin{wrapfigure}[20]{r}{5.5cm}
	\begin{tabular}{ | l | c | }
		\hline
		Number of nodes & $2344$  \\ \hline
		Number of payment channels & $16617$  \\ \hline
		Average degree & $7.0891$ \\ \hline
		Connected components & $2$  \\ \hline
		Density & $0.00605$ \\ \hline
		Total BTC held in LN & $543.61855$\bitcoinA\\ \hline
		s-metric& $0.6878$ \\ \hline
		Maximal independent set & $1564$ \\ \hline
		Bridges & $530$ \\ \hline
		Diameter & $6$ \\ \hline
		Radius & $3$ \\ \hline
		Mean shortest path &  $2.80623$ \\ \hline
		Transitivity& $0.1046$\\ \hline
		Average clustering coefficient&$0.304$ \\ \hline
		Degree assortativity& $-0.2690$ \\ \hline
	\end{tabular}
	\caption{LN at a glance: basic properties of the LN graph.}\label{fig:properties}
\end{wrapfigure}

@@

When a new node joins LN, it needs to select which other nodes it is trying to connect to. In every LN implementation one of the key goal of a node is to optimize its centrality by connecting to central nodes. This phenomena sets up a preferential attachment pattern. Betweenness centrality of a node $v$ is given by the expression $g(v)=\sum_{s\neq v \neq t}\frac{\sigma_{st}(v)}{\sigma_{st}},$ where $\sigma_{st}$ is the total number of shortest paths between node $s$ and $t$, whilst $\sigma_{st}(v)$ is the number of those paths, that pass through $v$. Closeness centrality  of a node $v$ is defined as $CC(u)=\frac{N}{\sum_{u\neq v}d(u,v)},$ where $N$ is the number nodes in the graph and $d(u,v)$ is the distance between node $u$ and $v$.  Closeness centrality measures how close a node is to all other nodes.

@@

\section{Robustness of LN}
It is a major question in network science how robust a given network is. LN, just like Bitcoin, is a permissionless network, where nodes can join and leave arbitrarily at any point in time. Nodes can also create new payment channels or close them any time. Furthermore as new payments are made, capacities of payment channels are changing steadily. Despite the dynamic nature of LN, its topology's characteristics remain constant after all.
In this section we investigate how resilient is LN, whether it can effectively withhold random node failures or deliberate attacks.
\subsection{Random Failures}
\begin{wrapfigure}[15]{r}{5.5cm}
	\begin{tabular}{ | l | c | }
		\hline
		Network & $f_c$  \\ \hline
		Internet & $0.92$  \\ \hline
		WWW & $0.88$ \\ \hline
		US Power Grid & $0.61$  \\ \hline
		Mobil Phone Call & $0.78$ \\ \hline
		E-mail & $0.92$ \\ \hline
		Science collaboration& $0.92$ \\ \hline
		E. Coli Metabolism & $0.96$ \\ \hline
		Yeast Protein Interactions & $0.88$ \\ \hline
		LN & $0.00535$ \\ \hline
	\end{tabular}
	\caption{Random failures in networks. Values of critical thresholds for other real networks are taken from \cite{barabasi2016network}.}\label{fig:randfailures}
\end{wrapfigure}

Random failures are a realistic attack vector for LN. If nodes happen to be off-line due to bad connections or other reasons, they can not participate in routing payments anymore. Such a failure can be modeled as if a node and its edges are removed from the graph. We continually remove nodes from the graph, until the networks is broken into several isolated components. The fraction of nodes need to be removed from a network to break it into multiple connected components is called critical threshold and denoted as $f_c$. As Figure~\ref{fig:randfailures}. displays LN is not capable of withstanding even random failures. This incapability is even more striking when compared to other real networks.

@@

We reasserted the targeted attack scenario, but for the second time we only removed one of the $30$ largest hubs and recorded the number of connected components. As it can be seen in Figure~\ref{fig:vertecconnectivity1removed} most of the hubs (25!) are so critical that their removal would be catastrophic for LN, namely they would leave behind several disconnected components.

Such network fragmentations are unwanted in case of LN, because they would make payment routing substantially more challenging (one needs to split the payment over several routes) or even impossible (there would be no routes at all). An analogous dissolution would effectively render LN non-functional.

\subsection{Fixing LN's resilience against random failures and attacks}
Designing networks which are robust to random failures and targeted attacks appear to be a conflicting desire \cite{barabasi2016network}. For instance a star graph, the simplest hub and spoke network, is resilient to random failures. The removal of any set of spokes does not hurt the connectedness of the main component. However it can not withstand a targeted attack against its central node, since it would leave behind isolated spokes.

>>>>

\begin{abstract}
Bitcoin's Lightning Network (LN) is a scalability solution for Bitcoin, which allows transactions to be issued with negligible fees and settle transactions instantly at scale. In order to use LN, funds need to be locked in payment channels on the Bitcoin blockchain (Layer-1), that one may use them in LN (Layer-2). LN is comprised of many payment channels forming a payment channel network. LN's promise is that a few payment channels already enable anyone to efficiently, securely and privately route payments across the whole network. In this paper we quantify the structural properties of LN and argue that LN's current topological properties could have been ameliorated in order to enable LN to reach its true potential.  
\end{abstract}
\keywords{Bitcoin, Lightning Network, Network Topology, Payment Channel Network}

\section{Introduction}
Recently the Bitcoin \cite{nakamoto2008bitcoin} network celebrated its 10th anniversary. During these years Bitcoin gained a huge popularity due to its publicly verifiable, decentralized, permissionless and censorship-resistant nature. This tremendous popularity and increasing interest in Bitcoin pushed its network's throughput to its limits. Without further advancements, the Bitcoin network can only settle $7$ transactions per second (tps), while mainstream centralized payment providers such as Visa and Mastercard can process approximately \num[group-separator={,}]{40000} tps in peak hours. Moreover one might need to pay large transaction fees on the Bitcoin network, while also need to wait 6 new blocks to be published in order to be certain enough that the transaction is included in the blockchain.

@@

\textbf{Our contributions.} We empirically measure and describe LN's topology and show how robust it is against both random failures and targeted attacks. These findings suggest that how LN's topology could be ameliorated in order to achieve its true potential.
\section{Lightning Network's Topology}
\begin{wrapfigure}[20]{r}{5.5cm}
	\begin{tabular}{ | l | c | }
		\hline
		Number of nodes & $2344$  \\ \hline
		Number of payment channels & $16617$  \\ \hline
		Average degree & $7.0891$ \\ \hline
		Connected components & $2$  \\ \hline
		Density & $0.00605$ \\ \hline
		Total BTC held in LN & $543.61855$\bitcoinA\\ \hline
		s-metric& $0.6878$ \\ \hline
		Maximal independent set & $1564$ \\ \hline
		Bridges & $530$ \\ \hline
		Diameter & $6$ \\ \hline
		Radius & $3$ \\ \hline
		Mean shortest path &  $2.80623$ \\ \hline
		Transitivity& $0.1046$\\ \hline
		Average clustering coefficient&$0.304$ \\ \hline
		Degree assortativity& $-0.2690$ \\ \hline
	\end{tabular}
	\caption{LN at a glance: basic properties of the LN graph.}\label{fig:properties}
\end{wrapfigure}

@@

When a new node joins LN, it needs to select which other nodes it is trying to connect to. In every LN implementation one of the key goal of a node is to optimize its centrality by connecting to central nodes. This phenomena sets up a preferential attachment pattern. Betweenness centrality of a node $v$ is given by the expression $g(v)=\sum_{s\neq v \neq t}\frac{\sigma_{st}(v)}{\sigma_{st}},$ where $\sigma_{st}$ is the total number of shortest paths between node $s$ and $t$, whilst $\sigma_{st}(v)$ is the number of those paths, that pass through $v$. Closeness centrality  of a node $v$ is defined as $CC(u)=\frac{N}{\sum_{u\neq v}d(u,v)},$ where $N$ is the number of nodes in the graph and $d(u,v)$ is the distance between node $u$ and $v$.  Closeness centrality measures how close a node is to all other nodes.

@@

\section{Robustness of LN}
It is a major question in network science how robust a given network is. LN, just like Bitcoin, is a permissionless network, where nodes can join and leave arbitrarily at any point in time. Nodes can also create new payment channels or close them any time. Furthermore as new payments are made, capacities of payment channels are changing steadily. Despite the dynamic nature of LN, its topology's characteristics remain constant after all.
In this section we investigate how resilient is LN, whether it can effectively withhold random node failures or deliberate attacks.
\subsection{Random Failures}
\begin{wrapfigure}[15]{r}{5.5cm}
	\begin{tabular}{ | l | c | }
		\hline
		Network & $f_c$  \\ \hline
		Internet & $0.92$  \\ \hline
		WWW & $0.88$ \\ \hline
		US Power Grid & $0.61$  \\ \hline
		Mobil Phone Call & $0.78$ \\ \hline
		Science collaboration& $0.92$ \\ \hline
		E. Coli Metabolism & $0.96$ \\ \hline
		Yeast Protein Interactions & $0.88$ \\ \hline
		LN & $0.60$ \\ \hline
	\end{tabular}
	\caption{Random failures in networks. Values of critical thresholds for other real networks are taken from \cite{barabasi2016network}.}\label{fig:randfailures}
\end{wrapfigure}

Random failures are a realistic attack vector for LN. If nodes happen to be off-line due to bad connections or other reasons, they can not participate in routing payments anymore. Such a failure can be modeled as if a node and its edges are removed from the graph. We continually remove nodes from the graph, until the networks is broken into several isolated components. The fraction of nodes need to be removed from a network to break it into multiple connected components is called critical threshold and denoted as $f_c$. As Figure~\ref{fig:randfailures}. displays LN is fairly capable of withstanding random failures, however not as well as other real world networks.

@@

We reasserted the targeted attack scenario, but for the second time we only removed one of the $30$ largest hubs and recorded the number of connected components. As it can be seen in Figure~\ref{fig:vertecconnectivity1removed} most of the hubs, 25, would leave behind several disconnected components.

\begin{wrapfigure}[15]{r}{5.5cm}
	\begin{tabular}{ | l | c | }
		\hline
		Network & $f_c$  \\ \hline
		Internet & $0.16$  \\ \hline
		WWW & $0.12$ \\ \hline
		US Power Grid & $0.20$  \\ \hline
		Mobil Phone Call & $0.20$ \\ \hline
		Science collaboration& $0.27$ \\ \hline
		E. Coli Metabolism & $0.49$ \\ \hline
		Yeast Protein Interactions & $0.16$ \\ \hline
		LN & $0.07$ \\ \hline
	\end{tabular}
	\caption{Real networks under targeted attacks. Values of critical thresholds for other real networks are taken from \cite{barabasi2016network}.}\label{fig:randfailures}
\end{wrapfigure}

Such network fragmentations are unwanted in case of LN, because they would make payment routing substantially more challenging (one needs to split the payment over several routes) or even impossible (there would be no routes at all).

\subsection{Improving LN's resilience against random failures and attacks}
Designing networks which are robust to random failures and targeted attacks appear to be a conflicting desire \cite{barabasi2016network}. For instance a star graph, the simplest hub and spoke network, is resilient to random failures. The removal of any set of spokes does not hurt the connectedness of the main component. However it can not withstand a targeted attack against its central node, since it would leave behind isolated spokes.
